---
title: "Slides"
author: "Ally Hinton"
date: "2/25/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Steps in creating slides

- sign into github
- create a new repository
- go into rstudio and create a new project FROM a github repository
- File>New Project>Version Control>Git>paste url from github repository page
- Note: creating a separate project for your slides is good practice because it is publicly available
- New RMarkdown, select presetation instead of document (choose html ioslides)
- Save RMarkdown as "index.html" -- this is important, make sure its lowercase
- push them to github: on the GIT tab in the upper right hand window in Rstudio
  - select all files and commit (must commit the index.html, other items are optional)
  - select push after commiting
  - enter github username and password
- Go to settings in GitHub and scroll down to "GitHub Pages", then change Source None to Master Branch
- copy url above this option "Your site is ready to be published at https://etc
- click edit on main page and put the url link into the Website box, and you can add a Description 

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

